Enter our title here

### 2017-08-14 manuscript.tex
Update manuscript.tex

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
open source R software package that allows students to learn R programing in their R console. This interactive learning tool contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.

@@

DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
free community courses and specialized 'Premium' classes that you need to purchase. However, when used for academic purposes
the premium DataCamp content if free.. (i'll come back to this).

>>>>

With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition 
to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. These tools 
allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}. 
*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
but this is not avaiblable for the classroom setting (coursera website) so should I include this?*

@@

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can 
create their own courses that coincide with their lessons and students can access the course without having to install R. 
The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this). 
When you create a free classroom group on the DataCamp website, you can add student's to the group and assign pre-existing 
course or a course that you've created for the particular class.

A feature that set's DataCamp courses apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a 
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration.
